---
title: "Assignment 1"
author: "Jessica Jagdeo and Jenny Balmagia"
date: "2/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
```

#### Create function: See R script with function waterstorage() in Assignment 1 folder
```{r}
## Water balance/storage equation

# Function describing water stored in a watershed/year using simplified inflow/outflow processes
# Function assumptions: The user must provide watershed_size in square miles and precipitation, evaporation, and runoff in inches per year

waterstorage = function(precip, evap, runoff, watershed_size) {
  storage = ((precip - (evap + runoff)) * 0.0833333) * (watershed_size * 27880000) 
  # Multiply by watershed size to get volumetric storage from rate inputs: precip, evap, runoff
  # Multiple watershed_size (given by user in square miles) by 27,880,000 to convert to square feet
  # Multiply precip - (evap + runoff) (given by user in inches) by 0.0833333 to convert to feet
  precip = ifelse((precip < 0), return("Precipitation must be greater than or equal to zero"), precip)
  evap = ifelse((evap < 0), return("Evaporation cannot be negative"), evap)
  runoff = ifelse((runoff < 0), return("Runoff cannot be negative"), runoff)
  return(storage)
  # Storage is returned in units of cubic feet per year
}
```

#### Generate sample data for water balance function
```{r}
# Generate first set of sample data to test funtion
nsample = 100

# Data created for a 10 sq mile watershed
# sample precipitation data, inches/year
precip = rnorm(mean = 7, sd = 2, n = nsample)
# sample evaporation data, inches/year
evap = rnorm(mean = 0.5, sd = 0.15, n = nsample)
# sample runoff data, inches/year
runoff = rnorm(mean = 0.7, sd = 0.2, n = nsample)

# Create dataframe to store results
results = data.frame(precip_in = precip, evap_in = evap, runoff_in = runoff, storage_ft3 = NA)


# Generate second set of sample data to test function
nsample2 = 200

# Data created for a 20 sq mile watershed
# Sample precip data, inches/year
precip2 = sample(x = 20:50, size = nsample2, replace = TRUE)
# Sample evap data, inches/year
evap2 = sample(x = 10:15, size = nsample2, replace = TRUE)
# Sample runoff data, inches/year
runoff2 = sample(x = 5:20, size = nsample2, replace = TRUE)

# Create dataframe to store results
results2 = data.frame(precip_in = precip2, evap_in = evap2, runoff_in = runoff2, storage_ft3 = NA)
```

#### Test waterstorage() function with sample data
```{r}
# Testing function for first set of sample data and 10 sq mile watershed
results$storage_ft3 = waterstorage(results$precip_in, results$evap_in,results$runoff_in, watershed_size = 10)


# Testing function for second set of sample data and 20 sq mile watershed
results2$storage_ft3 = waterstorage(results2$precip_in, results2$evap_in, results2$runoff_in, watershed_size = 20)
```

#### Plot results from waterstorage() function
```{r}
# Plotting results from first set of generated data

results1_plot <- results %>% 
  mutate(year = seq(1901, 2000, by = 1)) %>%  # Generating a series of years for plotting purposes
  ggplot(aes(x = year, y = storage_ft3/1000)) +
  geom_point(color = "darkgreen") +
  geom_line(color = "darkgreen") +
  theme_classic() +
  labs(x = "Year",
       y = expression(paste("Water Storage in 1000 ft"^"3"))) +
  ggtitle("Water Storage from Generated Data 1") +
  scale_y_continuous(labels = scales::comma) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))

results1_plot
```

Figure 1. Water storage of a watershed with an area of 10 square miles using randomly generated data for a random period of 1901 to 2000. The amount of water stored in this watershed, based on the randomly generated precipitation, evaporation, and runoff data, varies from 50,000 to 250,000 thousand cubic feet per year. 

```{r}
# Plotting results from second set of generated data

results2_plot <- results2 %>% 
  mutate(year = seq(1801, 2000, by = 1)) %>%  # Generating a series of years for plotting purposes
  ggplot(aes(x = year, y = storage_ft3/1000)) +
  geom_point(color = "darkblue") +
  geom_line(color = "darkblue") +
  theme_classic() +
  labs(x = "Year",
       y = expression(paste("Water Storage in 1000 ft"^"3"))) +
  ggtitle("Water Storage from Generated Data 2") +
  scale_y_continuous(labels = scales::comma) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))

results2_plot
```

Figure 2. Water storage of a watershed with an area of 20 square miles using randomly sampled data for a random period of 1801 to 2000. The amount of water stored in this watershed, based on the randomly sampled precipitation, evaporation, and runoff data, varies from -500,000 to 1,500,000 thousand cubic feet per year. The negative water storage implies water loss in this watershed. 