---
title: "Assignment 1"
author: "Jessica Jagdeo"
date: "2/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Assignment 1

With a partner

Write function to compute something that is of interest to you, make sure it has at least 2 inputs and several parameters

Add some error checking (at least two different kinds)

Save your function in a .R file

(Make sure you add comments to your function)

In an Rmarkdown document, generate sample data for your function in two different ways,

Apply the data to your function

Graph and add some text describing how to interpret the results

Upload both the function and the Rmarkdown file to your github - in a subfolder called Assignment 1

Add a link to your github site for Assignment 1 on Gauchospace

#### Create function: : See R scripts with function in Assignment 1 folder
```{r}

# Option 1: Water balance/storage equation

waterstorage = function(inflow, precip, evap, infiltrat, outflow) {
  storage = inflow + precip - evap - infiltrat - outflow
  precip = ifelse((precip < 0), return("Precipitation must be greater than or equal to zero"), precip)
  evap = ifelse((evap < 0), return("Evaporation cannot be negative"), evap)
  return(storage)
}

```

```{r}

# Option 2: Recurrence interval calculation

recurrence = function(total_yrs, magnitude_rank) {
  interval = ((1 + total_yrs)/magnitude_rank)
  total_yrs = ifelse((total_yrs < 0), return("Total years must be greater than zero"))
  return(interval)
}

```

#### Generate sample data
```{r}

nsample = 100
total_yrs = 100
max_annual_discharge = rnorm(mean=200, sd=10, n=nsample)
magnitude_rank = seq(1:100) # Trying to figure out how to assign magnitude rank based on generated max annual discharge

# Step 1  create data frame to store results 
# how many simulations, what do you want to keep

#create a dataframe that has rows for each model run
# columns for total years, max annual discharge generated, magnitude rank, and recurrence interval
results = data.frame(total_yrs = total_yrs, max_annual_discharge=max_annual_discharge, magnitude_rank = magnitude_rank, interval=NA)


```
