---
title: "Assignment 2"
author: "Jessica Jagdeo"
date: "3/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
```

Work in pairs

Write a function that takes as input:

a table that has prices for different fish
a table that has the number caught for each fish species for each location
each location is in a different column
each fish is in a different row

Function output will be:

most frequently caught fish in each location
total revenue for each location
total fisheries revenue sum
if user requests it graph of revenue by location and total revenue (as text)

Place your function in an *.R file

Generate some example data for your function; and show how this is created and used in an R markdown document Submit as usual as a git link on gauchospace

```{r}

# Generate a table that has prices for different fish

possible_fish = c("snapper","lionfish","grouper","hogfish","goatfish")

fish_cost <- as.data.frame(possible_fish) %>% 
  mutate(fish_prices = c(2, 4, 6, 8, 10))

# Generate a table that has the number caught for each species for each location:
## Each location is a different column
## Each fish is in a different row

fish_locations <- as.data.frame(possible_fish) %>% 
  mutate(Trinidad = sample(x = 10:50, size = 5, replace = TRUE),
         Jamaica = sample(x = 10:50, size = 5, replace = TRUE),
         Guyana = sample(x = 10:50, size = 5, replace = TRUE),
         Bahamas = sample(x = 10:50, size = 5, replace = TRUE),
         Barbados = sample(x = 10:50, size = 5, replace = TRUE)) 



```

Working on assignment with Jenny:

```{r}

#Price - Table that has prices for different fish ($/lb)

fish_price = data.frame(fish = c("Tuna","Swordfish","Salmon","Cod"), price = c(13, 9, 11, 6))

#Catch - Table that has the number caught for each fish species for each location 

possible_fish = c("Tuna", "Swordfish", "Salmon", "Cod")

fish_catch = data.frame(loc_A = sample(possible_fish, size = 20, replace = T), loc_B = sample(possible_fish, size = 20, replace = T), loc_C = sample(possible_fish, size = 20, replace = T))

#Additional sample data for catch by location:

fish_locations <- as.data.frame(possible_fish) %>% 
  mutate(Trinidad = sample(x = 10:50, size = 4, replace = TRUE),
         Jamaica = sample(x = 10:50, size = 4, replace = TRUE),
         Guyana = sample(x = 10:50, size = 4, replace = TRUE),
         Bahamas = sample(x = 10:50, size = 4, replace = TRUE),
         Barbados = sample(x = 10:50, size = 4, replace = TRUE))

#test

fish_info(catch = fish_locations, price = fish_price) # For some reason, it seems to be returning the min fish caught at each location...?

fish_catch = as.factor(fish_catch)
which.max(summary(fish_catch$loc_B))

```

